A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-25 paper/main.tex
revision of (cluster) results

% 2nd lvl and 3rd lvl
The second-level analysis which averaged contrast estimates across the eight stimulus segments per subject was carried out using a fixed effects model by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{woolrich2004multilevel, woolrich2008robust}.
Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a corrected cluster significance threshold of p<.05 \citep{woolrich2008robust}.
Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
% COPE 1:
Figure \ref{fig:results} depicts the results of the three contrasts (all Z-Threshold Z>3.4; p<.05 cluster-corrected).
The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded four significant clusters (see Table \ref{tab:cope1}):
one left laterlized cluster spanning from the angular gyrus and inferior posterior supramarginal gyrus across the superior and middle temporal gyrus, including parts of Heschl's gyrus and planum temporale.
A second left cluster in (inferior) frontal regions, including precentral gyrus, pars opercularis (Brodman Areal 44; BA44) and pars triangularis (BA45).
Similarly in the right hemisphere, one cluster spanning from the angular gyrus across the superior and middle temporal gyrus but including frontal inferior regions (pars opercularis and pars triangularis).
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded 9 significant clusters (see Table \ref{tab:cope3}):
one left laterlized cluster spanning from the angular gyrus across planum temporale and superior temporal gyrus, partially covering the Heschl's gyrus, into the anterior middle temporal gyrus.
A largely congruent but smaller cluster in the right hemisphere.
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
Three small clusters in the right occipital pole, right Heschl's gyrus and left superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded 3 significant clusters (see Table \ref{tab:cope5}):
two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction. In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hermisphere into the anterior part of superior temporal cortex.
Finally, two small right lateralized clusters in posterior cingulate gyrus and precuneus.

\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure.}
\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
\label{fig:results}
\end{figure*}

>>>>

% 2nd lvl
The second-level analysis which averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier de-weighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold
Z>3.4; p<.05 cluster-corrected).
% COPE 1:
The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded
four significant clusters (see Table \ref{tab:cope1}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus and inferior
posterior supramarginal gyrus across the superior and middle temporal gyrus,
including parts of Heschl's gyrus and planum temporale.
% cluster 2
A second left cluster in (inferior) frontal regions, including precentral gyrus,
pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
% cluster 3
Similarly in the right hemisphere, one cluster spanning from the angular gyrus
across the superior and middle temporal gyrus but including frontal inferior
regions (pars opercularis and pars triangularis).
% cluster 4
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded 9 significant
clusters (see Table \ref{tab:cope3}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus across planum
temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
into the anterior middle temporal gyrus.
% cluster 2
A largely congruent but smaller cluster in the right hemisphere.
% cluster 3 & 5, and 4 & 6
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
% remaining 3 clusters of COPE 3
Three small clusters in the right occipital pole, right Heschl's gyrus and left
superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded 4 significant clusters (see Table \ref{tab:cope5}):
% cluster 1 & 2
two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction. In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hermisphere into the anterior part of superior temporal cortex.
% cluster 3 & 4
Finally, two small right lateralized clusters in the right posterior cingulate
gyrus and right precuneus.

\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure}
\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
\label{fig:results}
\end{figure*}
